### 2024-12-29 mixed-models.qmd
20241229 - clean up code

```{r}
player_stats_seasonal_offense_subset$fantasyPointsPosNoZeros <- player_stats_seasonal_offense_subset$fantasyPointsPos <- player_stats_seasonal_offense_subset$fantasyPoints
player_stats_seasonal_offense_subset$fantasyPointsPos[player_stats_seasonal_offense_subset$fantasyPoints < 0] <- 0
player_stats_seasonal_offense_subset$fantasyPointsPosNoZeros[player_stats_seasonal_offense_subset$fantasyPoints <= 0] <- 0.01

@@

fantasyPointsVectorPosNoZeros <- fantasyPointsVectorPos <- fantasyPointsVector
fantasyPointsVectorPos[fantasyPointsVector < 0] <- 0
fantasyPointsVectorPosNoZeros[fantasyPointsVector <= 0] <- 0.01
```

@@

# positive-only
fit.exp <- fitdist(fantasyPointsVectorPos, "exp")

# positive and no zeros
fit.gamma <- fitdistrplus::fitdist(fantasyPointsVectorPosNoZeros, "gamma")
fit.lognormal <- fitdistrplus::fitdist(fantasyPointsVectorPosNoZeros, "lnorm")
fit.weibull <- fitdistrplus::fitdist(fantasyPointsVectorPosNoZeros, "weibull")

@@

model_gamma <- glm(
  formula = fantasyPointsPosNoZeros ~ 1,
  family = Gamma(),
  data = player_stats_seasonal_offense_subset,
  maxit = 100000)

@@

#### Prepare Data {#sec-fantasyPointsByAgeExperienceModelsBayesianPrepareData}

```{r}
player_stats_seasonal_offense_subset$fantasyPoints_posOnly <- player_stats_seasonal_offense_subset$fantasyPoints
player_stats_seasonal_offense_subset$fantasyPoints_posOnly[which(player_stats_seasonal_offense_subset$fantasyPoints_posOnly < 0)] <- 0
```

>>>>

```{r}
player_stats_seasonal_offense_subset$fantasyPoints_posOnlyNoZeros <- player_stats_seasonal_offense_subset$fantasyPoints_posOnly <- player_stats_seasonal_offense_subset$fantasyPoints
player_stats_seasonal_offense_subset$fantasyPoints_posOnly[player_stats_seasonal_offense_subset$fantasyPoints < 0] <- 0
player_stats_seasonal_offense_subset$fantasyPoints_posOnlyNoZeros[player_stats_seasonal_offense_subset$fantasyPoints <= 0] <- 0.01

@@

fantasyPointsVector_posOnlyNoZeros <- fantasyPointsVector_posOnly <- fantasyPointsVector
fantasyPointsVector_posOnly[fantasyPointsVector < 0] <- 0
fantasyPointsVector_posOnlyNoZeros[fantasyPointsVector <= 0] <- 0.01
```

@@

# positive-only
fit.exp <- fitdist(fantasyPointsVector_posOnly, "exp")

# positive and no zeros
fit.gamma <- fitdistrplus::fitdist(fantasyPointsVector_posOnlyNoZeros, "gamma")
fit.lognormal <- fitdistrplus::fitdist(fantasyPointsVector_posOnlyNoZeros, "lnorm")
fit.weibull <- fitdistrplus::fitdist(fantasyPointsVector_posOnlyNoZeros, "weibull")

@@

model_gamma <- glm(
  formula = fantasyPoints_posOnlyNoZeros ~ 1,
  family = Gamma(),
  data = player_stats_seasonal_offense_subset,
  maxit = 100000)

@@
